Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-10-29 hpca15/hpca2015-rebuttal.txt

Review-A

Overhead compared to previous literature (see review for references)

Consistency between checking coprocessor and processor.

1. How is your monitoring architecture (minus the partial monitoring support) different than one 
proposed in "Decoupling Dynamic Information Flow Tracking with a Dedicated Coprocessor"
by Kozyrakis et al.?

2. Do you guarantee to detect violations at instruction boundaries?

3. What is your exact definition of monitoring overhead?

4. Have you assessed the physical memory metadata requirements for monitors you designed?

5. Have you considered a design where the monitor uses a RAW microprocessor like fabric 
as opposed to a FIFO for communication?

Compare to Raksha.

What about false negatives?

Previous SW results that show low overheads.

Review-B

False negatives

Design space choice: Is it possible to use another core for monitoring tasks.

Review-C

For run time monitoring can you provide any precise guarantees regarding dropped requests (w/ the slack policy)?

Is hardware support really necessary? Partial monitoring with software
instrumentation (Sec 5.6 or [15])?

[7] has similarities to our approach.

Review-D

How does this compare to FADE?

How much better does this do than ad-hoc filtering in terms of error? (I believe Flexitaint also did some amount of drop-on-overhead policy)

Review-E

Advances over FADE

Measure coverage in terms of errors that were detected (i.e. false negative rate)

Review-F

Could you compare energy consumed by full and partial monitors?

Track invalid tags through different threads in multi-processor system? Coherence for dataflow monitor?

False negatives
Paper assumes that error/attacks are uniformly distributed across checks. Why is this a valid assumption?  It is possible that portions of execution that incur high monitoring overhead (say the ones with frequent monitoring events) would always not get checked. So you might never find bugs in such portions even if you monitor several executions.

How are the sources identified for the source-only dropping scheme? How and when do you decide drop the source?

Describe the hardware used to estimate slack.

Software tools have done sampling (see review for references).

### 2014-10-30 hpca15/hpca2015-rebuttal.txt

Common Questions

-Review-D,E: How does this compare to FADE?
Our main contribution in this work is an architecture which enables partial
monitoring (i.e., trade-off between coverage and overheads). We are not the
first to introduce null metadata filtering as a method for reducing monitoring
overheads. For example, FADE [11] introduces hardware to do this. However, we
show that our hardware support for partial monitoring is able to support null
metadata filtering with minor modifications. Thus, it is not necessary to
implement the full FADE hardware in order to add null metadata filtering to our
architecture for partial monitoring.

-Review-A,B,E,F: Evaluation of false negatives/error detection rate.
While we could not evaluate real errors/attacks due to difficulty in setting up
a large number of bugs and exploits and/or running real-world applications on
our simulation infrastructure, we believe that the percentage of checks
provides a good initial estimate of detection probability when errors/attacks
are uniformly distributed across checks. It will be interesting as future work
to evaluate the system with real-world bugs to see if this distribution holds
or if there exists correlations between bug locations and slack.

@@

Review-A

-Comparison to Raksha and [Kannan DSN 2009].
Raksha and the architecture proposed in [Kannan DSN 2009]
provide hardware architectures for information flow tracking. These
architectures have very low overheads because they are designed for a specific
monitoring technique.  Although Raskha provides some programmability in the
information flow tracking policy, it does not support the wide range of
monitors supported by our architecture (e.g., race detection).

-Do you guarantee to detect violations at instruction boundaries?
We do not guarantee when violations are detected. However, previous work by
[Deng et al. ICCD 2011] has described how precise exceptions can be supported
on a monitoring architecture similar to ours.

-What is your exact definition of monitoring overhead?
Monitoring overhead is the increase in execution time of the system running
monitoring compared to without monitoring.

-Have you assessed the physical memory metadata requirements for monitors you designed?
The worst-case memory usage can be determined based on the size of metadata per
memory location. We have not evaluated the actual memory usage, but previous
work on the implemented monitoring techniques have looked at this.

-Have you considered a design where the monitor uses a RAW microprocessor like fabric 
as opposed to a FIFO for communication?
A FIFO provides a simple solution for providing buffered communication between
the main core and the monitor.

@@

Review-B

-Design space choice: Is it possible to use another core for monitoring tasks.
The monitoring task is performed by another core (with the exception of the
FPGA-based monitor that was evaluated). However, in order to minimize the
performance impact of dropping a monitoring event, this was implemented using
custom hardware. In the past, we have explore performing these dropping
operations in software. However, this was almost as expensive as performing the
full monitoring operations and so was not effective at creating a trade-off
between coverage and performance.

@@

Review-C

-For run time monitoring can you provide any precise guarantees regarding
 dropped requests (w/ the slack policy)?
Dropping is decided based on run-time overheads (i.e., slack). This is
difficult to predict a priori and so we are not able to give precise guarantees
on what is dropped or the coverage achieved.

-Is hardware support really necessary? Partial monitoring with software
instrumentation (Sec 5.6 or [15])? Higher overhead/coverage ratio, but with
scaling out to many users, does it matter?
A software solution is cheaper to implement. However, if the overhead/coverage
ratio is too high, then the number of users needed to detect an error could be
prohibitively high. Table 1 shows that the gap in overhead between software and
hardware solutions for full monitoring can be an order of magnitude.

-[7] has similarities to our approach.
Our baseline architecture is similar to the one proposed by [7] and other
related work. Our work shows how partial monitoring can be supported on these
architectures using a dataflow engine.

@@

Review-D

-How much better does this do than ad-hoc filtering in terms of error?
Previous work uses filtering to reduce the overheads of monitoring. However,
they are not able to say anything about the overheads seen, especially with new
applications. The overheads can vary wildly (see Figure 9). Our architecture
allows a specified overhead to be targeted.

Review-E
See common questions.

@@

Review-F

-Could you compare energy consumed by full and partial monitors? 
We have not evaluated the difference in energy consumed by full and partial
monitors. It is not clear which uses more energy and it largely depends on the
number of events dropped and thus the overhead target. If everything is
dropped, then less energy is used since the dataflow engine operates on
single-bit flags and is more energy-efficient than the monitor. However, if no
events are dropped or filtered out, then the dataflow engine adds energy usage
above the baseline full monitoring because it adds additional operations to be
performed.

-Tracking invalid tags through different threads in multi-processor system?
 Coherence for dataflow monitor?
Invalid tags for different threads would be tracked by the dataflow engine
through shared memory, similar to shared data for multi-threaded programs. A
multi-processor implementation of the architecture would require coherence for
the caches of the dataflow engine and monitor, similar to the coherence needed
for the cores.

-How are the sources identified for the source-only dropping scheme? How and
when do you decide drop the source?
Sources can be identified by instruction type or by the programmer/compiler.
For example, for uninitialized memory check, all store instructions are
configured to be marked as sources. Alternatively, instructions can be marked
as source events by the programmer or compiler. For example, this is done for
array bounds check when pointers are initialized to mark these points as
sources. Dropping sources can be done based on slack or using a probabilistic
approach.

### 2014-10-30 hpca15/hpca2015-rebuttal.txt

Common Questions

-Review-D,E: How does this compare to FADE?
Our main contribution in this work is an architecture which enables partial
monitoring (i.e., trade-off between coverage and overheads). We are not the
first to introduce null metadata filtering as a method for reducing monitoring
overheads (e.g., FADE). However, we show that our hardware support for
partial monitoring is able to support null metadata filtering with minor
modifications. Thus, it is not necessary to implement the full FADE hardware in
order to add null metadata filtering to our architecture for partial
monitoring.

@@

-Review-A,B,E,F: Evaluation of false negatives/error detection rate.
While we could not evaluate real errors/attacks due to difficulty in setting up
a large number of bugs and exploits and/or running real-world applications on
our simulation infrastructure, we believe that the percentage of checks
provides a good initial estimate of detection probability when errors/attacks
are uniformly distributed across checks. It will be interesting as future work
to evaluate the system with real-world bugs to see if this distribution holds
or if there exists correlations between bug locations and slack.

Review-A

-Comparison to Raksha and [Kannan DSN2009].
Raksha and the architecture proposed in [Kannan DSN2009]
provide hardware architectures for information flow tracking. These
architectures have very low overheads because they are designed for a specific
monitoring technique.  Although Raskha provides some programmability in the
information flow tracking policy, it does not support the wide range of
monitors supported by our architecture (e.g., race detection).

-Do you guarantee to detect violations at instruction boundaries?
We do not guarantee when violations are detected. However, previous work by
[Deng ICCD2011] has described how precise exceptions can be supported
on a monitoring architecture similar to ours.

-Definition of monitoring overhead?
Monitoring overhead is the increase in execution time of a program running
monitoring compared to without monitoring.

-Have you assessed the physical memory metadata requirements?
The worst-case memory usage can be determined based on the size of metadata per
memory location. We have not evaluated the actual memory usage, but previous
work on the implemented monitoring techniques have looked at this.

-Have you considered using a RAW-like fabric as opposed to a FIFO for
communication?
A FIFO provided a simple solution for buffered communication between the main
core and the monitor.

@@

Review-B

-Use another core for monitoring tasks.
The monitoring task is performed by another core. However, dropping operations
were implemented using custom hardware (i.e., dataflow engine) in order to
minimize their performance impact. We have explored performing these dropping
operations in software. However, this can be almost as expensive as performing
the full monitoring operations and so was not effective at creating a trade-off
between coverage and performance.

@@

Review-C

-Can you provide any precise guarantees regarding dropped requests?
Dropping is decided based on run-time overheads (i.e., slack). This is
difficult to predict a priori and so we are not able to give precise guarantees
on what is dropped or the coverage achieved.

-Is hardware support really necessary? Higher overhead/coverage ratio, but with
scaling out to many users, does it matter?
Previous work that performs partial monitoring in software [15, 1] applied it
to more coarse-grained monitoring techniques instead of the fine-grained
instruction-level monitoring we target.  Table 1 shows that the gap in
overhead between software and hardware solutions for fine-grained monitoring
can be an order of magnitude.  Although a software solution is easier to
deploy, if the overhead/coverage ratio is too high, then the number of users
needed to detect an error or the minimum overhead to achieve any coverage could
be prohibitively high.

-[7] has similarities to your approach.
Our baseline architecture is similar to the one proposed by [7] and other
related work. However, our work is the first to show how partial monitoring can
be supported on these architectures using a dataflow engine.

@@

Review-D

-How much better does this do than ad-hoc filtering in terms of error?
Previous work uses filtering to reduce the overheads of monitoring. However,
they are not able to say anything about the overheads seen, especially with new
applications. These overheads can vary wildly (see Figure 9). Our architecture
allows a specified overhead to be targeted. FlexiTaint [Venkataramani HPCA2008]
does not have a drop-on-overhead policy.

Review-E

-Should we be measuring coverage in terms of errors detected, false positives
that were generated?
In terms of errors detected, see the response in Common Questions. Our
architecture does not generate any false positives.

@@

Review-F

-Energy consumed by full and partial monitors.
We have not evaluated the difference in energy consumed by full and partial
monitors. Dropping an event is less energy than performing full monitoring, but
the dataflow engine also adds energy overhead when not dropping. Thus, it is
not clear which uses more energy and it largely depends on the overhead
target and the number of events dropped.

-Tracking invalid tags through different threads in multi-processor system?
 Coherence for dataflow monitor?
Invalid tags for different threads would be tracked by the dataflow engine
through shared memory. A multi-processor implementation of the architecture
would require coherence for the caches of the dataflow engine and monitor,
similar to the coherence needed for the core caches.

-How are the sources identified? How do you decide to drop the source?
Sources are identified by instruction type.
For example, for uninitialized memory check, all store instructions are
configured to be marked as sources. In addition, custom instructions used for
setting metadata (e.g., setting array bounds metadata) are always marked as
sources. Dropping sources can be done based on slack or using a probabilistic
approach.

### 2014-10-31 hpca15/hpca2015-rebuttal.txt

-Review-D,E: How does this compare to FADE?
Our main contribution in this work is an architecture which enables partial
monitoring (i.e., trade-off between coverage and overheads). We are not the
first to introduce null metadata filtering as a method for reducing monitoring
overheads (e.g., FADE). However, we show that our hardware support for
partial monitoring is able to support null metadata filtering with minor
modifications. Thus, it is not necessary to implement the full FADE hardware in
order to add null metadata filtering to our architecture for partial
monitoring.

-Review-A,B,E,F: Evaluation of false negatives/error detection rate.
While we could not evaluate real errors/attacks due to difficulty in setting up
a large number of bugs and exploits and/or running real-world applications on
our simulation infrastructure, we believe that the percentage of checks
provides a good initial estimate of detection probability when errors/attacks
are uniformly distributed across checks. It will be interesting as future work
to evaluate the system with real-world bugs to see if this distribution holds
or if there exists correlations between bug locations and slack.

Review-A

-Comparison to Raksha and [Kannan DSN2009].
Raksha and the architecture proposed in [Kannan DSN2009] provide hardware
architectures for information flow tracking. These architectures show low
overheads because they are designed for a specific monitoring technique.
Although Raskha provides some programmability in the information flow tracking
policy, it does not support the wide range of monitors supported by our
architecture.

-Do you guarantee to detect violations at instruction boundaries?
We do not guarantee when violations are detected. However, previous work [Deng
ICCD2011] has described how precise exceptions can be supported on such an
architecture.

@@

Review-B

-Using another core for monitoring tasks.
The monitoring task is performed by another core. Dropping operations were
implemented using custom hardware in order to minimize their performance
impact. We have explored performing these dropping operations in software.
However, this can lead to high overheads even when all events are dropped.

@@

Review-C

-Can you provide any precise guarantees regarding dropped requests?
Dropping is decided based on run-time overheads. This is difficult to predict a
priori and so we are not able to give precise guarantees on what is dropped or
the coverage achieved.

-Is hardware support really necessary? Higher overhead/coverage ratio, but with
scaling out to many users, does it matter?
Table 1 shows that the gap in overhead between software and hardware solutions
for fine-grained monitoring can be an order of magnitude. Although a software
solution is easier to deploy, if the overhead/coverage ratio is too high, then
the number of users needed to detect an error or the minimum overhead to
achieve any coverage can be prohibitively high.

@@

-[7] has similarities to your approach.
Our baseline architecture is similar to the one proposed by [7] and other
related work. However, our work is the first to show how partial monitoring can
be supported on these architectures using a dataflow engine.

Review-D

-How much better does this do than ad-hoc filtering?
Previous work uses filtering to reduce the overheads of monitoring. However,
the overheads seen can vary wildly (see Figure 9). Our architecture allows a
target overhead to be specified. FlexiTaint [Venkataramani HPCA2008] does not
mention a drop-on-overhead policy.

@@

Review-E

-Should we be measuring coverage in terms of errors detected, false positives
 generated?
For errors detected, see Common Questions. Our architecture does not generate
any false positives.

@@

Review-F

-Energy consumed by full and partial monitors.
Dropping an event is less energy than performing full monitoring, but
the dataflow engine also adds energy overhead when not dropping. Thus, it is
not clear which uses more energy and it largely depends on the overhead
target and the number of events dropped.

-Tracking invalid tags through different threads? Coherence for dataflow
 monitor?
Invalid tags for different threads would be tracked by the dataflow engine
through shared memory. A multi-processor implementation of the architecture
would require coherence for the caches of the dataflow engine and monitor,
similar to the coherence needed for the core caches.

-How are sources identified? How do you decide to drop the source?
Sources are identified by instruction type. For example, for uninitialized
memory check, all store instructions are configured to be marked as sources. In
addition, custom instructions used for setting metadata (e.g., setting array
bounds metadata) are always marked as sources. Dropping sources can be done
based on slack or using a probabilistic approach.

-Sample-based software tools.
Sampling-based methods typically can reduce overheads but overheads can vary
across applications. Results typically show that average overheads are low but
can include outliers. This is not surprising as the overheads without sampling
can vary (see Figure 9). Our architecture allows an overhead target to be
specified.

### 2014-10-31 hpca15/hpca2015-rebuttal.txt

Common Questions

-Review-D,E: How does this compare to FADE?
Our main contribution in this work is an architecture which enables partial
monitoring (i.e., trade-off between coverage and overheads). We are not the
first to introduce null metadata filtering as a method for reducing monitoring
overheads (e.g., FADE). However, we show that our hardware support for
partial monitoring is able to support null metadata filtering with minor
modifications. Thus, it is not necessary to implement the full FADE hardware in
order to add null metadata filtering to our architecture for partial
monitoring.

-Review-A,B,E,F: Evaluation of false negatives/error detection rate.
While we could not evaluate real errors/attacks due to difficulty in setting up
a large number of bugs for multiple monitoring schemes,
we believe that the percentage of checks
provides a good initial estimate of detection probability when errors/attacks
are uniformly distributed across checks. It will be interesting as future work
to evaluate the system with real-world bugs to see if this distribution holds
or if there exists correlations between bug locations and slack.

@@

Review-A

-Comparison to Raksha and [Kannan DSN2009].
Raksha and the architecture proposed in [Kannan DSN2009] provide hardware
architectures for information flow tracking. These architectures show low
overheads because they are designed for a specific monitoring technique.
Although Raskha provides some programmability in the information flow tracking
policy, it does not support the wide range of monitors supported by our
architecture.

-Guarantee to detect violations at instruction boundaries?
We do not enforce a check to be done before the monitored instruction finishes.
However, previous work [Deng ICCD2011] described how precise exceptions can be 
supported on such decoupled architecture.

@@

Review-B

-Using another core for monitoring?
We explored performing monitoring on another core and FPGA fabric. Dropping operations were
implemented using custom hardware in order to minimize their performance
impact. We explored performing the dropping operations in software, but
found that that design leads to high overheads even when all events are dropped.

@@

Review-C

-Provide any precise guarantees regarding dropped requests?
The system does not provide strict guarantees on the overhead, but can closely
match the target in practice. Because run-time overheads are difficult to
predict a priori, there is no precise guarantee on what is dropped.

-Is hardware support really necessary? 
We found that hardware support is necessary to closely match the overhead
target (source dropping in software is insufficient) and provide meaningful coverage 
with low overhead. High per-system coverage is also important when the goal
is to provide a partial protection for individual systems.

@@

Review-E

-Measuring coverage in errors detected? False positives?
For errors detected, see Common Questions. Our architecture does not generate
any false positives.

Review-F

-Energy consumed by full and partial monitors.
In our baseline monitoring architecture, monitoring uses another core and 
has the power consumption comparable to that of the main core. On the other hand,
the power consumption of the dropping hardware is often less than 10% of
the main core power consumption. Therefore, our architecture certainly saves
energy when monitoring operations are dropped. However, when almost no monitoring
operation is dropped, we found that the dropping hardware incurs a small
energy overhead.
We will add more explicit energy comparisons.

-Tracking invalid tags through different threads? Coherence for dataflow
 monitor?
Invalid tags for different threads would be tracked by the dataflow engine
through shared memory. A multi-processor implementation of the architecture
would require coherence for the meta-data, similar to what have been studied
for LBA and Raksha.

-How are sources identified? How do you decide to drop the source?
Sources are identified by instruction type or explicit SW instructions. 
For example, for uninitialized
memory check, all store instructions are configured to be marked as sources. In
addition, custom instructions used for setting metadata (e.g., setting array
bounds metadata) are marked as sources. Dropping sources can be done
based on slack or using a probabilistic approach.

### 2014-10-31 hpca15/hpca2015-rebuttal.txt

-Review-A,B,E,F: Evaluation of false negatives/error detection rate.
While we could not evaluate real errors/attacks due to difficulty in setting up
a large number of bugs for multiple monitoring schemes, we believe that the
percentage of checks provides a good initial estimate of detection probability
when errors/attacks are uniformly distributed across checks. It will be
interesting as future work to evaluate the system with real-world bugs to see
if this distribution holds or if there exists correlations between bug
locations and slack.

Review-A

-Comparison to Raksha and [Kannan DSN2009].
Raksha and the architecture proposed in [Kannan DSN2009] provide hardware
architectures for information flow tracking. These architectures show low
overheads because they are designed for a specific monitoring technique.
Although Raskha provides some programmability in the information flow tracking
policy, it does not support the wide range of monitors supported by our
architecture.

-Guarantee to detect violations at instruction boundaries?
We do not enforce a check to be done before the monitored instruction finishes.
However, previous work [Deng ICCD2011] described how precise exceptions can be 
supported on such decoupled architectures.

@@

-Measuring coverage in errors detected? False positives?
For errors detected, see Common Questions. Our architecture does not generate
any false positives.

Review-F

-Energy consumed by full and partial monitors.
In our baseline monitoring architecture, monitoring uses another core and 
has the power consumption comparable to that of the main core. On the other hand,
the power consumption of the dropping hardware is often less than 10% of
the main core power consumption. Therefore, our architecture certainly saves
energy when monitoring operations are dropped. However, when almost no monitoring
operation is dropped, we found that the dropping hardware incurs a small
energy overhead. We will add more explicit energy comparisons.

-Tracking invalid tags through different threads? Coherence for dataflow
 monitor?
Invalid tags for different threads would be tracked by the dataflow engine
through shared memory. A multi-processor implementation of the architecture
would require coherence for the metadata, similar to what has been studied
for LBA and Raksha.

@@

-How are sources identified? How do you decide to drop the source?
Sources are identified by instruction type or explicit SW instructions. For
example, for uninitialized memory check, all store instructions are configured
to be marked as sources. In addition, custom instructions used for setting
metadata (e.g., setting array bounds metadata) are marked as sources. Dropping
sources can be done based on slack or using a probabilistic approach.

-Sampling-based software tools.
Sampling-based methods can reduce overheads but overheads can vary
across applications. Results typically show that average overheads are low but
can include outliers. This is not surprising as the overheads without sampling
can vary (see Figure 9). Our architecture allows an overhead target to be
specified.

### 2014-12-17 related.tex
Fix up related work formatting.

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and
dynamic information flow tracking\cite{testudo-micro08}.
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, which is one of the target applications of our architecture.
% Limited Monitoring
In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. 
Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring to meet deadlines for hard real-time systems.

>>>>

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and
dynamic information flow tracking~\cite{testudo-micro08}.
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, which is one of the target applications of our architecture.
% Limited Monitoring
In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. 
Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring to meet deadlines for hard real-time systems.
